Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-18 paper.Rmd
today's talk was excellent

1.2.1 Gather and prepare data
```{r}
#Reading and saving data
source("./R/list_apt_files.R")
file_names <- list_apt_files()
open_sky <- map_dfr(file_names, read_csv)
#write_csv(open_sky, "./data/open_sky.csv")
```

@@

#Filtering Brazilian and European data to reduce the sample (and csv) size
#Preparing airports file

bra_10_apts <- c("SBBR", "SBGR", "SBSP", "SBKP", "SBRJ", "SBGL", "SBCF", "SBSV", "SBPA", "SBCT")
eur_apts <- c("EHAM","LFPG","EGLL","EDDF","EDDM","LEMD","LIRF","LEBL","EGKK","LSZH")
study_airports <- c(bra_10_apts, eur_apts)
study_airports

fb2 <- fb2 %>% filter(origin %in% bra_10_apts | destination %in% bra_10_apts) %>% mutate(REG = "BRA", .before = typecode)
fb2
summary(fb2)

>>>>

1.2.1 Gather and prepare data
```{r}
#Reading raw data protocol

source("./R/list_apt_files.R")
year <- "2021"
file_names <- list_apt_files(.year = year)
open_sky <- map_dfr(file_names, read_csv)
fb1 <- open_sky %>% transmute(typecode = as.factor(typecode), origin = as.factor(origin), destination = as.factor(destination), firstseen, lastseen) %>% drop_na()

#write_csv(open_sky, "./data/open_sky.csv")

#Reading prepared data
open_sky <- read_csv("data/open_sky.csv")
```

@@

#Filtering Brazilian and European data to reduce the sample (and csv) size
#Preparing airports file
#Here we can control the selective sample

bra_10_apts <- c("SBBR", "SBGR", "SBSP", "SBKP", "SBRJ", "SBGL", "SBCF", "SBSV", "SBPA", "SBCT")
eur_apts <- c("EHAM","LFPG","EGLL","EDDF","EDDM","LEMD","LIRF","LEBL","EGKK","LSZH")
study_airports <- c(bra_10_apts, eur_apts)

fb3 <- fb2 %>% filter(origin %in% study_airports | destination %in% study_airports)

base_dataset <- fb3 %>% mutate(BRA_ORIGIN = origin %in% bra_10_apts,
                        BRA_DEST = destination %in% bra_10_apts,
                        EUR_ORIGIN = origin %in% eur_apts,
                        EUR_DEST = destination %in% eur_apts,
                        BRA_EUR_DIRECT = (origin %in% bra_10_apts | destination %in% bra_10_apts) & (origin %in% eur_apts | destination %in% eur_apts))

# I opened a lot of logical variables to facilitate us knowing how many flights there are

summary(base_dataset)

temp1 <- base_dataset %>% group_by(
  YR = year(firstseen),
  ADEP = origin,
  ADES = destination) %>%
  summarise(COUNT = n(), .groups = "drop") %>%
  arrange(desc(COUNT)) %>%
  transmute(ROUTE = paste(ADEP, ADES, sep = "-"), YR, COUNT) %>%
  group_by(YR) %>%
  slice_head(n = 15)
temp1

temp1 %>% ggplot(aes(x = COUNT)) +
  geom_col(aes(y = ROUTE)) +
  facet_grid(.~YR)
